A graph-based data model for interactive evolutionary computation

### 2017-01-19 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Human centered conceptual framework

\section{IEC Graph based model}
\label{sec:graph}
The fundamental goal of this research is to develop a user-centered framework
for interactive evolutionary computation (IEC) in order to increase users’
participation and also to minimize the amount of evaluations needed for the
evolutionary process in given Web-based IEC application.  This framework is 
presented in figure \ref{fig:uc_framework}. The current model is tailored 
to the EvoSpace-I functionality and capabilities but it can be modified to 
handle other platforms, just by adding new clases of nodes.

@@

The user centered framework consists of three high level components:

\begin{itemize}
  \item { \tt Interactive Evolutionary Computational system.}  
  This is the real world system that we are going to model, it consist of
  human users and their interaction with one or more individuals from
  the population, this could be through a device, user interface or
  by directly interacting with real world objects generated as part of the algorithm.

>>>>

\section{IEC Human-centered framework}
\label{sec:graph}
The general goal of this research is to develop a human-centered [cite] framework
for interactive evolutionary computation (IEC) in order to increase
participation and also to minimize the amount of evaluations needed for the
evolutionary process in given IEC application. We deliberately use the more general
term Human instead of User, because humans are not always playing the role of
users in software engineering sense, they could just be interacting 
naturaly with their environment and with out knowing they are implicitly
evaluating a possible solution. In other cases the evaluation could be done
by the natural interactions of a group of humans in a collaborative fashion
or not. For instance the IEC algorithm could by trying to optimize 
the design of an exit sign in an airport, then the quality of this sign could be
determined by the average the time it takes a sample of people to 
find the exit. In this example there could be certain collaboration
between users if they are not traveling alone, of course this is only one of
the considerations designers could make.

%I will keep it general for this section -Mario
%The current model is tailored 
%to the EvoSpace-I functionality and capabilities but it can be modified to 
%handle other platforms, just by adding new clases of nodes.

@@

The human centered framework consists of three high level components depicted
in figure \ref{fig:uc_framework}:

\begin{itemize}
  \item { \tt Interactive Evolutionary Computational system.}  
  This is the real world system that we are going to model, it consist of
  human users and their interactions with one or more individuals from
  the population. There are many ways in which humans could interact 
  with indivuals, this could be through a mobile device, a user interface 
  or by interacting with real world objects generated as part of the algorithm.
  There is also the posibility that fitness is or part of the search is done
  in devices lended by the human. The information gathered through the 
  interaction will guide the search.

% We could reference Nod
